Ornaments as indicators of social changes in northeastern Taiwan before and after the European colonial period

### 2020-07-09 analysis/paper/paper.Rmd
knits on BM's computer!

# join two dataset to get coordinate
ornaments_period_join <-
  ornaments_period_clean %>%
  mutate(period = as.factor(period)) %>% # seems need this line first
  group_by(Pit_No, period) %>%
  count(Categories) %>%
  inner_join(AD_data, by = c("Pit_No" = "坑號"))

# create df for all types of ornaments by units and period
ornaments_period_join_all_type_across_periods <-
  ornaments_period_join %>% 
  group_by(period, Pit_No, geometry) %>% 
  summarize(n = sum(n))

>>>>

# join two dataset to get coordinate
ornaments_period_join <-
  ornaments_period_clean %>%
  mutate(period = as.factor(period)) %>% # seems need this line first
  group_by(Pit_No, period) %>%
  count(Categories) %>%
  ungroup %>% 
  inner_join(AD_data, by = c("Pit_No" = "坑號"))

# create df for all types of ornaments by units and period
ornaments_period_join_all_type_across_periods <-
  ornaments_period_join %>% 
  group_by(period, 
           Pit_No
           #,geometry
          ) %>% 
  summarize(n = sum(n)) %>% 
  ungroup %>% 
  inner_join(AD_data %>% 
               select(坑號, geometry), by = c("Pit_No" = "坑號"))
